---
title: "NOR-SOLIDARITY DMC report"
author: "Inge Christoffer Olsen, PhD"
date: '`r format(Sys.time(), "%d %B, %Y")` '
output: word_document
params:
  viedoc_export: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(ggplot2)
library(ggformula)
library(wesanderson)
library(purrr)
library(rlang)
library(glue)
#library(kableExtra)
library(knitr)

```

```{r load-datasets, include = FALSE}

tddm <- read_rds("data/td/tddm.rds")
tdran <- read_rds("data/td/tdran.rds")
raw <- read_rds("data/raw/raw.rds")
adsl <- read_rds("data/ad/adsl.rds")
adeff <- read_rds("data/ad/adeff.rds")
adae <- read_rds("data/ad/adae.rds")
tdex <- read_rds("data/td/tdex.rds")
```


# Introduction
This is the report for the Data Monitoring Committee meeting in the NOR-SOLIDARITY trial.  The data are based on an export from the Viedoc electronic data capture system time stamped "`r params$viedoc_export`". There were `r n_distinct(adsl)` included patients.

# Inclusion status

## Inclusion rate


```{r inclusionplot, echo = FALSE}
adsl %>% 
  arrange(randt) %>% 
  mutate(n = row_number()) %>% 
  gf_line(n ~ randt, color = wes_palette(n=1, name = "Darjeeling1")) %>% 
  gf_theme(theme = theme_classic()) %>% 
  gf_labs(y = "Number randomised", x = "Date")
```

## Inclusion by hospital

```{r by-site, echo = FALSE}


adsl %>% group_by(sitename) %>% 
  mutate(n=n()) %>% 
  arrange(-n) %>%  
  gf_bar(~ reorder(sitename, -n), fill = wes_palette(n=1, name = "Darjeeling1")) %>% 
  gf_theme(theme = theme_classic() ) %>% 
  gf_theme(axis.text.x = element_text(angle = 45, hjust = 1)) %>% 
  gf_labs(x = "", y = "Number randomised")

```

## By treatment

```{r by-treatment, echo = FALSE}



adsl %>% group_by(rantrt) %>% summarise(n=n(), .groups = "drop_last") %>% 
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")) +
  theme_classic() + 
  theme(legend.position = "none") + 
  labs(x="", y = "Number randomised")


```

\newpage

# Demographics

```{r dm-functions}
mean_sd <- function(data, var, group, digits = 1) {
  var <- ensym(var)
  group <- ensym(group)
  data %>% 
    group_by(!!group) %>% 
    summarise(mean = mean(!!var, na.rm = TRUE), 
              sd = sd(!!var, na.rm = TRUE), 
              missing = sum(is.na(!!var))
              , .groups = "drop_last") %>% 
    mutate_at(vars(mean, sd), ~round(., digits = digits)) %>% 
    mutate(txt = paste0(mean, " (", sd, ")")) %>% 
    select(group, txt) %>% 
    deframe
}


n_pct <-  function(data, var, group, level = 1) {
  var <- ensym(var)
  group <- ensym(group)
  data %>% 
    filter(!is.na(!!var)) %>% 
    group_by(!!group, !!var) %>% 
    summarise(n = n(), 
              .groups = "drop_last") %>% 
    group_by(!!group) %>% 
    mutate(tot = sum(n),
           pct = round(n/tot*100,digits = 1)) %>% 
    mutate(txt = paste0(n, " (", pct, "%)")) %>% 
    filter(!!var == !!level) %>% 
    ungroup %>% 
    select(group, txt) %>% 
    deframe
}

empty <- function(data, var, group, ...){
  group <- ensym(group)
  data %>% 
    group_by(!!group) %>% 
    summarise(n = n(), 
              .groups = "drop_last") %>% 
    mutate(txt = "") %>% 
    select(group,txt) %>% 
    deframe
}

stats_exec <- function(f, data, var, group, ...){
    rlang::exec(f, data, var, group, !!!(...))
}

```

```{r headers}
arms <- c("SOC", "SOC + HCQ", "SOC + Remdesivir")
total_n <- n_distinct(adsl$subjectid)

header <- adsl %>%
  group_by(rantrt, subjectid) %>%
  summarise(n=n(), .groups = "drop_last") %>%
  group_by(rantrt) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  ungroup() %>%
  mutate(armtxt = arms) %>%
  mutate(txt = paste0(armtxt, " (N=", n, ")")) %>%
  select(txt) %>%
  deframe


```



```{r demographics, warning = FALSE, message = FALSE, results = 'asis', echo = FALSE}

dm_table <- tribble(
  ~text, ~f, ~var, ~param,
  "Age (years)", "mean_sd", "age_calc", list(digits = 1), 
  "Female, n (%)", "n_pct", "sex", list(level = "Female")
)



dm_table %>%
  mutate(data = list(adsl),
         group = "rantrt") %>%
  mutate(res = pmap(list(f, data, var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, all_of(levels(adsl$rantrt))) %>%
  knitr::kable(col.names = c("Parameter", header),
               caption = "Demographics")

```

# Exposure

```{r exposure, results = "asis", echo = FALSE}

adsl %>%
  select(sitename, sitecode, subjectid, dmicdat, dmage, randt, rantrt) %>%
  left_join(tdex, by = c("sitename", "sitecode", "subjectid")) %>%
  group_by(subjectid, rantrt) %>%
  summarise(totdose_hcq = sum(dabcno),
            n_dose_hcq = sum(dabcno > 0),
            n_desc_hcq = sum(dadiyn_c =="Yes"),
            totdose_rem = sum(drremds),
            n_dose_rem = sum(drremds >0),
            n_desc_rem = sum(dardisc == "Yes"),
            .groups = "drop_last") %>%
  filter(rantrt != "Standard of care (SOC)") %>%
  mutate(totdose = if_else(rantrt == "Hydroxychloroquine + SOC", totdose_hcq, totdose_rem),
         n_dose = if_else(rantrt == "Hydroxychloroquine + SOC", n_dose_hcq, n_dose_rem),
         n_desc = if_else(rantrt == "Hydroxychloroquine + SOC", n_desc_hcq, n_desc_rem),
         any_desc = n_desc > 0) %>%
  group_by(rantrt) %>%
  summarise(median_totdose = quantile(totdose, 0.5, na.rm = TRUE),
            q1_totdose = quantile(totdose, 0.25, na.rm = TRUE),
            q3_totdose = quantile(totdose, 0.75, na.rm = TRUE),
            median_no_doses = median(n_dose,0.5,  na.rm = TRUE),
            q1_no_doses = quantile(n_dose, 0.25, na.rm = TRUE),
            q3_no_doses = quantile(n_dose, 0.75, na.rm = TRUE),
            n_anydesc = sum(any_desc, na.rm = TRUE),
            n = n(),
            .groups = "drop_last") %>%
  mutate(`Total dose, median (IQR), mg` = glue("{median_totdose} ({q1_totdose} - {q3_totdose})"),
         `Days with treatment, median (IQR)` = glue("{median_no_doses} ({q1_no_doses} - {q3_no_doses})"),
         `Patients with any treatment discrepencies, n (%)` = glue("{n_anydesc} ({round(100*n_anydesc/n, digits = 1)}%)")) %>%
  select(-(median_totdose:n)) %>%
  pivot_longer(-rantrt) %>%
  pivot_wider(names_from = rantrt, values_from = value) %>%
  rename(Parameter = name) %>%
  knitr::kable(booktabs = TRUE,
               caption = "Exposure to study treatment")



```



# Adverse Events

```{r ae-fn}
ae_n_pct <-  function(data, var, group, level = 1) {
  var <- ensym(var)
  group <- ensym(group)

  data %>%
    group_by(subjectid, !!group, !!var) %>%
    summarise(n = sum(!!var),
              .groups = "drop_last") %>%
    group_by(!!group, !!var) %>%
    summarise(n_ae = sum(n),
            n_pat = n(),
            .groups = "drop_last") %>%
    group_by(!!group) %>%
    mutate(N_pat = sum(n_pat),
           pct = round(n_pat/N_pat*100,digits = 1),
           txt = paste0(n_pat, " (", pct, "%)")) %>%
    filter(!!var %in% !!level) %>%
    ungroup %>%
    select(!!group, txt) %>%
    deframe
}

ae_N_n_pct <-  function(data, var, group, level = 1) {
  var <- ensym(var)
  group <- ensym(group)

  data %>%
    group_by(subjectid, !!group) %>%
    summarise(n = sum(!!var),
              .groups = "drop_last") %>%
    mutate(!!var := if_else(n==0, 0, 1)) %>%
    group_by(!!group, !!var) %>%
    summarise(n_ae = sum(n),
            n_pat = n(),
            .groups = "drop_last") %>%
    group_by(!!group) %>%
    mutate(N_pat = sum(n_pat),
           pct = round(n_pat/N_pat*100,digits = 1),
           txt = paste0("[", n_ae,"] ", n_pat, " (", pct, "%)")) %>%
    mutate(txt = if_else(n_ae == 0, "[0] 0 (0%)", txt)) %>%
    filter(!!var %in% !!level) %>%
    ungroup %>%
    select(!!group, txt) %>%
    deframe
}

stats_exec <- function(f, data, var, group, ...){
    rlang::exec(f, data, var, group, !!!(...))
}
```

## AE Summary

```{r ae-summary}

ae_summary_table <- tribble(
    ~text,  ~var, ~f,
  "Number of AEs", "anyae", "ae_N_n_pct",
  "Number of patients with any AEs?", "anyae", "ae_n_pct",
  "Number of patients with one AE", "one_ae", "ae_n_pct",
  "Number of patients with two AE", "two_ae", "ae_n_pct",
  "Number of patients with three or more AEs", "three_plus_ae", "ae_n_pct",
  "Number of SAEs", "sae", "ae_N_n_pct",
  "Number of patients with any SAEs?", "anysae","ae_n_pct"
)

tmp<-ae_summary_table %>%
  mutate(data = list(adae),
         group = "rantrt",
         param = list(level = 1)) %>%
  mutate(res = pmap(list(f, data, var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  mutate(id = paste0("txt", id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, starts_with("txt")) %>%
  knitr::kable(col.names = c("Parameter", header),
        caption = "Summary of Adverse Events")

tmp
```

The numbers are [Number of events] Number of patients (percentage of patients), or Number of patients (percentage of patients)


## By System Organ Class and Preferred Term

```{r aetab1}
ae_table_fns <- function(data, filtervar){

  filtervar = ensym(filtervar)

  data %>%
    group_by(rantrt) %>%
    mutate(N_pat = n_distinct(subjectid)) %>%
    filter(!!filtervar == 1)  %>%
    group_by(subjectid, rantrt, N_pat, soc_name, pt_name) %>%
    summarise(n_ae = n(),
              .groups = "drop_last") %>%
    filter(!is.na(pt_name)) %>%
    group_by(rantrt, N_pat, soc_name, pt_name) %>%
    summarise(n_pat = n(),
              n_ae = sum(n_ae),
              .groups = "drop_last") %>%
    mutate(pct = round(n_pat/N_pat*100,digits = 1),
           txt = paste0("[", n_ae,"] ", n_pat, " (", pct, "%)"),
           arm = rantrt) %>%
    ungroup %>% select(arm, soc_name, pt_name, txt) %>%
    pivot_wider(values_from = txt, names_from = arm, values_fill = list(txt = "")) %>%
    #mutate_at(vars(starts_with("arm")), ~if_else(is.na(.), "", .)) %>%
    arrange(soc_name, pt_name) %>%  group_by(soc2 = soc_name) %>%
    mutate(soc_name = if_else(row_number() != 1, "", soc_name)) %>% ungroup() %>% select(-soc2) %>%
    filter(soc_name != "NA")
}

adae %>%
  bind_rows(adae, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  mutate(all = 1) %>%
  ae_table_fns("all") %>%
  knitr::kable(col.names = c("System Organ Class", "Preferred Term", header),
               caption = " Adverse Events by System Organ Class and Preferred term", longtable = TRUE, booktabs = TRUE) #%>%
  #column_spec(1:2, width = "5cm")
```

## Serious Adverse Events

```{r saetab}

adae %>%
  bind_rows(adae, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  ae_table_fns("aesercd") %>%
  knitr::kable( col.names = c("System Organ Class", "Preferred Term", header),
               caption = "Serious Adverse Events by System Organ Class and Preferred term",
         booktabs = TRUE,
         longtable = TRUE) #%>%
  #column_spec(1:2, width = "5cm")

```

## Suspected Unexpected Serious Adverse Reaction

```{r susar}

adae %>%
  bind_rows(adae, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  mutate(susar = (aesercd == 1) & (saerelcd == 2) & saeexpcd ==2) %>%
  ae_table_fns("susar") %>%
  rename( "System Organ Class" = soc_name,  "Preferred Term" = pt_name) %>%
  knitr::kable(
               caption = "Suspected Unexpected Serious Adverse Reaction by System Organ Class and Preferred term",
         booktabs = TRUE,
         longtable = TRUE)

```

# Mortality and other outcomes by admission state

```{r}
adeff %>%
  group_by(sq_admis, outcome) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  group_by(sq_admis) %>%
  mutate(tot = sum(n),
           pct = round(n/tot*100,digits = 1)) %>%
  mutate(txt = paste0(n, " (", pct, "%)")) %>%
  ungroup %>%
  select(-(n:pct)) %>%
  pivot_wider(values_from = txt, names_from = sq_admis) %>%
  knitr::kable( booktabs = TRUE, caption = "Outcome")

```




<!-- # Outcome -->

<!-- The following report is based on pseudo-randomised groups, not true allocations. The true allocations are available for the DMC only. -->

<!-- ```{r outcome} -->

<!-- adeff %>% -->
<!--   mutate(rantrt = sample(rantrt, n(), replace = FALSE)) %>% #Delete this row for true allocations -->
<!--   group_by(rantrt, outcome) %>% -->
<!--   summarise(n = n(), .groups = "drop_last") %>% -->
<!--   group_by(rantrt) %>% -->
<!--   mutate(tot = sum(n), -->
<!--            pct = round(n/tot*100,digits = 1)) %>% -->
<!--   mutate(txt = paste0(n, " (", pct, "%)")) %>% -->
<!--   ungroup %>% -->
<!--   select(-(n:pct)) %>% -->
<!--   pivot_wider(values_from = txt, names_from = rantrt) %>% -->
<!--   knitr::kable(col.names = c("Parameter", header), booktabs = TRUE, caption = "Outcome") -->


<!-- ``` -->

