---
title: "NOR-SOLIDARITY First Interim Report"
author: "Inge Christoffer Olsen, PhD"
date: '`r format(Sys.time(), "%d %B, %Y")` '
output:
  word_document:
    reference_docx: report_template.docx
    toc: TRUE
params:
  viedoc_export: ous_20201016_084109
  pseudorandom: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(ggformula)
library(wesanderson)
library(rlang)
library(glue)
library(knitr)
library(labelled)
library(survival)
library(survminer)

```

```{r load-datasets, include = FALSE}

tddm <- read_rds("data/td/tddm.rds")
tdran <- read_rds("data/td/tdran.rds")
raw <- read_rds("data/raw/raw.rds")
adsl <- read_rds("data/ad/adsl.rds")
adex <- read_rds("data/ad/adex.rds")
adeff <- read_rds("data/ad/adeff.rds")
adae <- read_rds("data/ad/adae.rds")
tdex <- read_rds("data/td/tdex.rds")
addm <- read_rds("data/ad/addm.rds")
adev <- read_rds("data/ad/adev.rds")
tdds <- read_rds("data/td/tdds.rds")

source("src/External/functions.R", local = knitr::knit_global())
export_date = substr(params$viedoc_export,5,19) %>% lubridate::as_datetime()
if(params$pseudorandom) {
  pr_text = "While the results are based on real data, the treatment allocation has been drawn randomly for this report. Thus, this is a mock-up report intended to show how the final report will look like, without showing the actual results of the trial and the treatment differences."
} else {
  pr_text = "The results in this report is according to the true random allocation. "
}
```


# Introduction
This is the report for the first interim analysis of the NOR-SOLIDARITY trial. The data are based on an export from the Viedoc electronic data capture at "`r export_date`" system time stamped "`r params$viedoc_export`". `r pr_text` There were `r n_distinct(adsl)` included patients.

# Inclusion status

## Inclusion rate


```{r inclusionplot, echo = FALSE}
adsl %>%
  filter(fas == "Yes") %>%
  arrange(randt) %>%
  mutate(n = row_number()) %>%
  gf_line(n ~ randt, color = wes_palette(n=1, name = "Darjeeling1")) %>%
  gf_theme(theme = theme_classic()) %>%
  gf_labs(y = "Number randomised", x = "Date")
```

## Inclusion by hospital

```{r by-site, echo = FALSE}


adsl %>%
  filter(fas == "Yes") %>%
  group_by(sitename) %>%
  mutate(n=n()) %>%
  arrange(-n) %>%
  gf_bar(~ reorder(sitename, -n), fill = wes_palette(n=1, name = "Darjeeling1")) %>%
  gf_theme(theme = theme_classic() ) %>%
  gf_theme(axis.text.x = element_text(angle = 45, hjust = 1)) %>%
  gf_labs(x = "", y = "Number randomised")

```

## By treatment

```{r by-treatment, echo = FALSE}



adsl %>%
  filter(fas == "Yes") %>%
  group_by(rantrt) %>%
  summarise(n=n(), .groups = "drop_last") %>%
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(x="", y = "Number randomised (all) in FAS")

adsl %>%
  filter(fas_hcq == "Yes") %>%
  group_by(rantrt) %>%
  summarise(n=n(), .groups = "drop_last") %>%
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(x="", y = "Number randomised (HCQ available) in FAS")


adsl %>%
  filter(fas_rem == "Yes") %>%
  group_by(rantrt) %>%
  summarise(n=n(), .groups = "drop_last") %>%
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")[c(1,3)]) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(x="", y = "Number randomised (remdesivir available) in FAS")




```



```{r headers}
arms_tot <- c("SOC", "SOC + HCQ", "SOC + Remdesivir")
total_n <- n_distinct(adsl$subjectid)

arms_hcq <- arms_tot[c(1,2)]
arms_rem <- arms_tot[c(1,3)]
arms_all <- "All patients"

header <- function(data, arms){

 data %>%
  group_by(rantrt, subjectid) %>%
  summarise(n=n(), .groups = "drop_last") %>%
  group_by(rantrt) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  ungroup() %>%
  mutate(armtxt = arms) %>%
  mutate(txt = paste0(armtxt, " (N=", n, ")")) %>%
  select(txt) %>%
  deframe
}

header_tot <- adsl %>%
  filter(fas=="Yes") %>%
  header(arms_tot)

header_hcq <- adsl %>%
  filter(fas_hcq=="Yes") %>%
  header(arms_hcq)

header_rem <- adsl %>%
  filter(fas_rem=="Yes") %>%
  header(arms_rem)

header_all <- adsl %>% 
  filter(fas == "Yes") %>% 
  summarise(n=n(), .groups = "drop_last") %>% 
  mutate(txt = paste0("All patients (N=", n, ")")) %>% 
  select(txt) %>% 
  deframe

```


# Patient flow

```{r patient-flow, warning = FALSE}

adsl_all <- readr::read_rds("data/ad/adsl_all.rds")

fas_table <- tribble(
  ~text, ~f, ~var, ~param,
  "Enrolled", "n_pct", "enrolled", list(level = "Yes"),
  "Randomised", "n_pct", "randomised", list(level = "Yes"),
  "Included in FAS", "n_pct", "fas", list(level = "Yes"),
  "Excluded from FAS, No post-randomisation information", "n_pct", "fasex1", list(level = "Yes"),
  "Excluded from FAS, incorrect inclusion", "n_pct", "fasex2", list(level = "Yes")
  )

fas_table %>%
  mutate(data = list(adsl_all %>% mutate(tmp = "Enrolled")),
         group = "tmp") %>%
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, Enrolled) %>%
  knitr::kable(col.names = c("Parameter", "Total"),
               caption = "Patient flow total")

fas_table %>%
  filter(text != "Enrolled") %>%
  mutate(data = list(adsl_all),
         group = "rantrt") %>%
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, any_of(levels(adsl$rantrt))) %>%
  knitr::kable(col.names = c("Parameter", arms_tot),
               caption = "Patient flow by arm")

fas_table %>%
  filter(text != "Enrolled") %>%
  mutate(data = list(adsl_all %>% filter(ranavail_hcq == "Yes")),
         group = "rantrt") %>%
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, any_of(levels(adsl$rantrt))) %>% 
  select(-`Remdesivir + SOC`) %>% 
  knitr::kable(col.names = c("Parameter", arms_hcq),
               caption = "Patient flow by arm in HCQ")

fas_table %>%
  filter(text != "Enrolled") %>%
  mutate(data = list(adsl_all %>% filter(ranavail_rem == "Yes")),
         group = "rantrt") %>%
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, any_of(levels(adsl$rantrt))) %>%
  select(-`Hydroxychloroquine + SOC`) %>% 
  knitr::kable(col.names = c("Parameter", arms_rem),
               caption = "Patient flow by arm in Remdesivir")

adsl %>% 
  left_join(tdds, by = "subjectid") %>% 
  group_by(eosreas, rantrt) %>% 
  summarise(n = n(), .groups = "drop_last") %>% 
  pivot_wider(names_from = rantrt, values_from = n) %>% 
  mutate(across(where(is.integer), ~ if_else(is.na(.x), 0L, .x))) %>% 
  mutate(eosreas = str_trunc(as.character(eosreas), 40, ellipsis = ""),
         Total = `Standard of care (SOC)` + `Hydroxychloroquine + SOC` + `Remdesivir + SOC`) %>% 
  mutate(eosreas = if_else(is.na(eosreas), "Completed", eosreas)) %>% 
  rename(Reason = eosreas ) %>% 
  knitr::kable(caption = "Patient flow during study (FAS)")
  

adsl %>% 
  left_join(tdds, by = "subjectid") %>% 
  filter(fas_hcq == "Yes") %>% 
  group_by(eosreas, rantrt) %>% 
  summarise(n = n(), .groups = "drop_last") %>% 
  pivot_wider(names_from = rantrt, values_from = n) %>% 
  mutate(across(where(is.integer), ~ if_else(is.na(.x), 0L, .x))) %>% 
  mutate(eosreas = str_trunc(as.character(eosreas), 40, ellipsis = ""),
         Total = `Standard of care (SOC)` + `Hydroxychloroquine + SOC`) %>% 
  mutate(eosreas = if_else(is.na(eosreas), "Completed", eosreas)) %>% 
  rename(Reason = eosreas ) %>% 
  knitr::kable(caption = "Patient flow during study (FAS) in HCQ")

adsl %>% 
  left_join(tdds, by = "subjectid") %>% 
  filter(fas_rem == "Yes") %>% 
  group_by(eosreas, rantrt) %>% 
  summarise(n = n(), .groups = "drop_last") %>% 
  pivot_wider(names_from = rantrt, values_from = n) %>% 
  mutate(across(where(is.integer), ~ if_else(is.na(.x), 0L, .x))) %>% 
  mutate(eosreas = str_trunc(as.character(eosreas), 40, ellipsis = ""),
         Total = `Standard of care (SOC)` + `Remdesivir + SOC`) %>% 
  mutate(eosreas = if_else(is.na(eosreas), "Completed", eosreas)) %>% 
  rename(Reason = eosreas ) %>% 
  knitr::kable(caption = "Patient flow during study (FAS) in Remdesivir")

```


# Demographics


```{r demographics, warning = FALSE, message = FALSE, results = 'asis', echo = FALSE}

dm_table <- tribble(
  ~text, ~f, ~var, ~param,
  "**Demographics**", "empty", "", list(),
  "  Age (years)", "mean_sd", "age_calc", list(digits = 1),
  "  Female, n (%)", "n_pct", "sex", list(level = "Female"),
  "  Body Mass Index (kg/m^2^)", "mean_sd", "vsbmi", list(digits = 0),
  "  Body Mass Index (kg/m^2^)", "median_iqr", "vsbmi", list(digits = 0),
  "  Symptoms prior to admission (days)", "mean_sd", "sympdur", list(digits = 1),
  "  P/F-ratio at admittance (kPa)", "mean_sd", "rcratio", list(digits = 0),
  "  P/F-ratio < 40kPa, n (%)", "n_pct", "rcratio40", list(level = "Yes"),
  "  Temperature (°C)", "mean_sd", "vstemp", list(digits = 1),
  "  Admitted to ward, n(%)", "n_pct", "sq_admis", list(level = "Ward"),
  "  Admitted to ICU, n(%)", "n_pct", "sq_admis", list(level = "ICU"),
  " WHO Moderate disease state (4-5), n(%)", "n_pct", "rcwhostate", list(level = "Moderate"),
  "  WHO Severe disease state (6-9), n(%)", "n_pct", "rcwhostate", list(level = "Severe"),
  "  WHO Severe disease state (6), n(%)", "n_pct", "rcwhocps", list(level = 6),
  "  WHO Severe disease state (5), n(%)", "n_pct", "rcwhocps", list(level = 5),
    "**Comorbidities**", "empty", "", list(),
  "  Chronic cardiac disease, including congenital heart disease", "n_pct", "cc_card", list(level = "Yes"),
  "  Chronic pulmonary disease, n(%)", "n_pct", "cc_copd", list(level = "Yes"),
  "  Ever smoking, n(%)", "n_pct", "cc_eversmoker", list(level = "Yes"),
  "  Hypertension, n(%)", "n_pct", "cc_ht", list(level = "Yes"),
  "  Diabetes, n(%)", "n_pct", "cc_diab", list(level = "Yes"),
  "  Obese (BMI > 30 kg/m^2^), n(%)", "n_pct", "vsobese", list(level="Obese"),
  "**Co-medications**", "empty", "", list(),
  "  Steroids", "n_pct", "me9", list(level = "Yes"),
  "  Other immunomodulatory drugs", "n_pct", "me10", list(level = "Yes"),
  "  ACE inhibitor", "n_pct", "me1", list(level = "Yes"),
  "  AT-II blockers", "n_pct", "me2", list(level = "Yes"),
  "**Hematology**", "empty", "", list(),
  "  Hemoglobin (g/dL)", "median_iqr", "lbhbres", list(digits = 1),
  "  WBC (x10^9^/L)", "median_iqr", "lbwbcres", list(digits = 1),
  "  Neutrophils (x10^9^/L)", "median_iqr", "lbneures", list(digits = 1),
  "  Lymphocytes (x10^9^/L)", "median_iqr", "lblymres", list(digits = 1),
  "  Platelet counts (x10^9/L)", "median_iqr", "lbpcres", list(digits = 1),
  "**Inflammatory markers**", "empty", "", list(),
  "  CRP (mg/L)", "median_iqr", "lbcrpres", list(digits = 1),
  "  Procalcitonin (µg/L)", "median_iqr", "lbprores", list(digits = 2),
  "  Ferritin (µg/L)", "median_iqr", "lbferres", list(digits = 1),
  "**Other**", "empty", "", list(),
  "  LDH (U/L)", "median_iqr", "lbldres", list(digits = 1),
  "  D-dimer (mg/L FEU)", "median_iqr", "lbdimres1", list(digits = 2),
  "  AST ", "median_iqr", "lbastres", list(digits = 1),
  "  ALT ", "median_iqr", "lbaltres", list(digits = 1),
  "  eGFR (mL/min/1.73 m^2^) ", "median_iqr", "lbegfrc", list(digits = 1),
  "**Viral count**", "empty", "", list(),
  "  Viral count (log~10~ counts/1000 cells)", "mean_sd", "vllog10cpkc", list(digits = 1),
  "**Anti-SARS-CoV-2 Antibodies**", "empty", "", list(),
  "  Sero converted (RBD ≥ 5)", "n_pct", "abseroc", list(level = "RBD ≥ 5"),
  "**Supplementary baseline information**", "empty", "", list(),
  "  Systolic Blood Pressure (mmHg)", "mean_sd", "vssys", list(digits = 0),
  "  Diastolic Blood Pressure (mmHg)", "mean_sd", "vsdia", list(digits = 0),
  "  Mean Arterial Blood Pressure (mmHg)", "mean_sd", "vsmap", list(digits = 0),
  "  SOFA score", "mean_sd", "scsumsc", list(digits = 1),
  "  Chronic kidney disease, n(%)", "n_pct", "cc_ckd", list(level = "Yes"),
  "  Autoimmune disease, n(%)", "n_pct", "cc_aid", list(level = "Yes"),
  "  Cognitive impairment/dementia, n(%)", "n_pct", "cc_cogn", list(level = "Yes"),
  "  Neurological disorder, n(%)", "n_pct", "cc_neur", list(level = "Yes"),
  "  Cancer, n(%)", "n_pct", "cc_cance", list(level = "Yes"),
  "  Cirrhosis, n(%)", "n_pct", "cc_cirr", list(level = "Yes"),
  "  Asthma, n(%)", "n_pct", "cc_asthm", list(level = "Yes"),
  "  HIV, n(%)", "n_pct", "cc_hiv", list(level = "Yes"),
  "  Active TB, n(%)", "n_pct", "cc_tb", list(level = "Yes"),
  "Note, all percentages are given with observed values in the denominator, missing values discarded   ", "empty", "", list()
)



dm_table_f <- function(data, table_temp, caption, header, group = "rantrt"){
table_temp %>%
  mutate(data = list(data),
         group = group) %>%
  mutate(res = pmap(list(f, data, var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, any_of(levels(adsl$rantrt)), any_of("Yes")) %>%
  knitr::kable(col.names = c("Parameter", header),
               caption = caption)
}


addm_hcq <- addm  %>% filter(fas_hcq == "Yes")
addm_rem <- addm  %>% filter(fas_rem == "Yes")

dm_table_f(addm, dm_table, "Demographics, all patients (FAS)", header_all, group = "fas")

dm_table_f(addm, dm_table, "Demographics, all arms (FAS)", header_tot)

dm_table_f(addm_hcq, dm_table, "Demographics, HCQ (FAS)", header_hcq)

dm_table_f(addm_rem, dm_table, "Demographics, Remdesivir (FAS)", header_rem)


missing_table <- dm_table %>%
  mutate(f = if_else(var == "", "empty","missing_f"))

dm_table_f(addm, missing_table, "Missing values, all arms (FAS)", header_tot)


```

# Exposure

```{r exposure, results = "asis", echo = FALSE}

ex_table <- tribble(
  ~text, ~f, ~var, ~param,
  "Total dose (mg), median (IQR)", "median_iqr", "extotdose", list(digits = 0),
  "Treatment duration, median (IQR)", "median_iqr", "extrtdur", list(digits = 0),
  "Number of doses given, median (IQR)", "median_iqr", "exndose", list(digits = 0),
  "Patients with any treatment discrepencies, n (%)	", "n_pct", "exdisc", list(level = "Yes")
  )

ex_table %>%
  mutate(data = list(adex %>% filter(fas == "Yes")),
         group = "rantrt") %>%
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, c("Hydroxychloroquine + SOC", "Remdesivir + SOC")) %>%
  knitr::kable(col.names = c("Parameter", header_tot[c(2,3)]),
               caption = "Exposure to study treatment")






```
# Efficacy

## Mortality

### Descriptives
```{r mortality-descriptives}



mort_desc_f <- function(filter_name = fas, caption){
adev %>% filter({{filter_name}} == "Yes") %>%
  group_by(rantrt, survcens) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(N =  sum(n),
         pct = round(n/N*100, digits = 1)) %>%
  filter(survcens =="No") %>%
  select(-survcens) %>%
  knitr::kable(col.names = c("Treatment", "# deaths", "# randomised", "%"), caption = caption)
}

mort_desc_f(caption = "All arms (FAS)")

mort_desc_f(fas_hcq, caption = "HCQ (FAS)")

mort_desc_f(fas_rem, caption = "Remdesivir (FAS)")


```
### Plots
```{r mortres-plots}
rdev <- read_rds("results/rds/rdev.rds")



rdev %>%
  mutate(title = glue::glue("{fname}, {dname}"),
         plot = map2(plot, title, ~ .x + ggtitle(.y)),
         walk(plot,print)) %>%
  invisible()

```

### Efficacy estimates

```{r mortres-est}


rdev %>%
   mutate(title = glue::glue("{fname}, {dname}")) %>%
  select(title, RR, pval) %>%
  knitr::kable(caption = "Relative risk estimates and p-values",
               col.names = c("Timeframe, Population", "Relative risk", "P-value"))


```


## Viral load

### Plots

```{r vl-plots, results = "asis", warning = FALSE}

rdvlrf <- readr::read_rds("results/rds/rdvlrf.rds")

rdvlrf %>%
  filter(seq == 1) %>% 
  mutate(walk(plot1, plot)) %>% 
  invisible()

rdvlrf %>%
  filter(seq == 1) %>% 
  mutate(walk(plot2, plot)) %>% 
  invisible()
  
  
```

### Marginal probability estimates by treatment group and difference

```{r vl-estimates, results = "asis"}

rdvlrf %>% 
  filter(seq == 1) %>% 
  pull(table) %>% 
  walk(print) %>% 
  invisible()



```

## Viral load subgroup analyses

### Plots, Hydroxychloroquine

```{r vl-sg-plots-hcq, results = "asis", warning = FALSE}

rdvl_sg <- readr::read_rds("results/rds/rdvl_sg.rds")

rdvl_sg %>%
  filter(population == "fas_hcq") %>% 
  mutate(walk(plot1, plot)) %>% 
  invisible()

rdvl_sg %>%
  filter(population == "fas_hcq") %>% 
  mutate(walk(plot2, plot)) %>% 
  invisible()
  
```

### Marginal probability estimates by treatment group and difference Hydroxychloroquine

```{r vl-sg-estimates-hcq, results = "asis"}

rdvl_sg %>% 
  filter(population == "fas_hcq") %>% 
  pull(table) %>% 
  walk(print) %>% 
  invisible()

```

### Plots Remdesivir

```{r vl-sg-plots-rem, results = "asis", warning = FALSE}

rdvl_sg <- readr::read_rds("results/rds/rdvl_sg.rds")

rdvl_sg %>%
  filter(population =="fas_rem") %>% 
  mutate(walk(plot1, plot)) %>% 
  invisible()

rdvl_sg %>%
  filter(population == "fas_rem") %>% 
  mutate(walk(plot2, plot)) %>% 
  invisible()
  
```



### Marginal probability estimates by treatment group and difference Remdesivir

```{r vl-sg-estimates-rem, results = "asis"}

rdvl_sg %>% 
  filter(population == "fas_rem") %>% 
  pull(table) %>% 
  walk(print) %>% 
  invisible()

```



## Respiratory failure by pO2/FiO2-ratio

### Plots

```{r rf-plots, results = "asis", warning = FALSE}

rdvlrf %>%
  filter(seq == 2) %>% 
  mutate(walk(plot1, plot)) %>% 
  invisible()
  
rdvlrf %>%
  filter(seq == 2) %>% 
  mutate(walk(plot2, plot)) %>% 
  invisible()

```

### Marginal probability estimates by treatment group and difference

```{r rf-estimates, results = "asis"}

rdvlrf %>% 
  filter(seq == 2) %>% 
  pull(table) %>% 
  walk(print) %>% 
  invisible()

```



## Dichotomous endpoints

### Descriptives


```{r dich-desc, results = "asis"}

rddi <- readr::read_rds("results/rds/rddi.rds")

rddi_tbl <- function(data, pop, text, id) {
  
  data %>%
    filter(pop_text == pop) %>%
    select(pop_text, Outcome = label, {{text}}, {{id}}) %>%
    unnest(c({{text}}, {{id}})) %>%
    pivot_wider(names_from = {{id}}, values_from = {{text}}) %>%
    select(-pop_text) 
  
}

rddi_tbl(rddi, "Hydroxychloroquine", desc_text, desc_id) %>% 
  knitr::kable(caption = "Hydroxycholoquine")
cat("Figures are number of patients with the outcome and percent (%)")

rddi_tbl(rddi, "Remdesivir", desc_text, desc_id) %>% 
  knitr::kable(caption = "Remdesivir")
cat("Figures are number of patients with the outcome and percent (%)")


```

### Marginal probability estimates by treatment group and difference

```{r dich-marg}
hcq_m <- rddi_tbl(rddi,"Hydroxychloroquine", marglev, marglev_id)
hcq_e <- rddi_tbl(rddi,"Hydroxychloroquine", margeff, margeff_id) 

hcq_m %>% 
  left_join(hcq_e, by = "Outcome") %>% 
  knitr::kable(caption = "Hydroxychloroquine")

rem_m <- rddi_tbl(rddi,"Remdesivir", marglev, marglev_id)
rem_e <- rddi_tbl(rddi,"Remdesivir", margeff, margeff_id) 

rem_m %>% 
  left_join(rem_e, by = "Outcome") %>% 
  knitr::kable(caption = "Remdesivir")


```




## Inflammatory laboratory parameters



```{r efflbres, results = "asis", echo = FALSE}
rdlb <- read_rds("results/rds/rdlb.rds")



lables <- rdlb %>% 
  select(var) %>% 
  distinct() %>% 
  mutate(label =case_when(
    var == "lbcrpres" ~  "CRP (mg/L)",
    var == "lbferres" ~  "Ferritin (µg/L)",
    var == "lbldres" ~   "LDH (U/L)",    
    var == "lblymres" ~  "Lymphocytes (x10^9/L)",
    var == "lbneures" ~  "Neutrophils (x10^9/L)",
    var == "lbprores" ~  "Procalcitonin (µg/L)",
  ))

efflbres <- rdlb %>%
  select(-label) %>% 
  full_join(lables, by="var") %>% 
  mutate(poptitle = if_else(population == "fas_hcq", "HCQ", "Remdesivir")) %>% 
  mutate(marginsplot = pmap(list(data = margins, ytitle = label), plot_cont_margins),
         title = glue::glue("{label}, {poptitle}"))


```

### Descriptives

```{r efflbres-desc, results = "asis"}
efflbres %>%
  mutate(walk2(descriptives, title, ~knitr::kable(.x, caption = .y) %>% print))  %>%
  invisible()

```

### Plots

```{r efflbres-plots, results = "asis"}
efflbres %>%
  mutate(marginsplot = map2(marginsplot, title, ~ .x + ggtitle(.y) ),
         walk(marginsplot, print))  %>%
  invisible()

```

### Efficacy estimates

```{r efflbres-est, results = "asis"}
efflbres %>%
  mutate(walk2(diffs, title,  ~knitr::kable(.x, caption = .y,
                                            col.names = c("Estimator",
                                                          "Treatment",
                                                          "Estimate",
                                                          "Lower 95% CL",
                                                          "Upper 95% CL",
                                                          "P-value"),
                                            digits = 3) %>%
                 print)
         )  %>%
  invisible()

```


## SARS-CoV2 antibodies at day 90

### Descriptives
```{r ab-desc, results = "asis", warning = FALSE, message = FALSE}

rdab <- readr::read_rds("results/rds/rdab.rds")

rdab_tbl <- function(data, pop, text, id) {
  
  data %>%
    filter(pop_text == pop) %>%
    select(seq, pop_text, Outcome = label, {{text}}, {{id}}) %>%
    unnest(c({{text}}, {{id}})) %>%
    pivot_wider(names_from = {{id}}, values_from = {{text}}) %>%
    select(-pop_text) 
  
}

rdab_dtbl <- function(pop){
  
rdab_tbl(rdab, pop, mean_text, id) %>%
  mutate(Statistic = "Mean (SD)") %>% 
  add_row(rdab_tbl(rdab, pop, median_text, id) %>% 
            mutate(Statistic = "Median (IQR)")) %>%
  select(Outcome, Statistic, everything()) %>% 
  arrange(seq, Statistic) %>% 
  group_by(seq) %>% 
  mutate(Outcome = if_else(row_number() == 1, Outcome, "")) %>% 
  ungroup() %>% 
  select(-seq) %>% 
  knitr::kable(caption = pop)

}

rdab_dtbl("Hydroxychloroquine")

rdab_dtbl("Remdesivir")

adab %>% filter(studyday>65) %>% mutate(antibodies  = if_else(abrbd >= 5, 1, 0)) %>% group_by(rantrt, subjectid) %>% summarise(antibodies = max(antibodies)) %>% group_by(rantrt) %>% summarise(tot = sum(antibodies), n = n()) %>% knitr::kable(caption = "Number of positive antibodies (rbd ≥ 5) by treatment group")

adab %>% filter(studyday>65 & fas_hcq == "Yes") %>% mutate(antibodies  = if_else(abrbd >= 5, 1, 0)) %>% group_by(rantrt, subjectid) %>% summarise(antibodies = max(antibodies)) %>% group_by(rantrt) %>% summarise(tot = sum(antibodies), n = n()) %>% knitr::kable(caption = "Number of positive antibodies (rbd ≥ 5) by treatment group in HCQ")

adab %>% filter(studyday>65 & fas_rem == "Yes") %>% mutate(antibodies  = if_else(abrbd >= 5, 1, 0)) %>% group_by(rantrt, subjectid) %>% summarise(antibodies = max(antibodies)) %>% group_by(rantrt) %>% summarise(tot = sum(antibodies), n = n()) %>% knitr::kable(caption = "Number of positive antibodies (rbd ≥ 5) by treatment group in Remdesivir")

```

### Marginal probability estimates by treatment group and difference

```{r ab-marg, results = "asis"}
hcq_m <- rdab_tbl(rdab,"Hydroxychloroquine", marglev, marglev_id)
hcq_e <- rdab_tbl(rdab,"Hydroxychloroquine", margeff, margeff_id) 

hcq_m %>% 
  left_join(hcq_e, by = "Outcome") %>% 
  select(-starts_with("seq")) %>% 
  knitr::kable(caption = "Hydroxychloroquine")
cat("Estimates are presented with 95% confidence limits")


rem_m <- rdab_tbl(rdab,"Remdesivir", marglev, marglev_id)
rem_e <- rdab_tbl(rdab,"Remdesivir", margeff, margeff_id) 

rem_m %>% 
  left_join(rem_e, by = "Outcome") %>% 
  select(-starts_with("seq")) %>% 
  knitr::kable(caption = "Remdesivir")
cat("Estimates are presented with 95% confidence limits")

```




## Time to last discharge

### HCQ

```{r discharge-hcq}
library(survival)
library(survminer)
adev_hcq <- adev %>% filter(fas_hcq == "Yes")
fit_hcq  <- surv_fit(Surv(dischargeday, dischargecens == "No") ~ rantrt, 
                      data = adev_hcq)

ggsurvplot(fit_hcq, data = adev_hcq, fun = "event", pval = TRUE)

fit_hcq_28  <- surv_fit (Surv(dischargeday_28, dischargecens_28 == "No") ~ rantrt, 
                      data = adev_hcq)

ggsurvplot(fit_hcq_28, data = adev_hcq, fun = "event", pval = TRUE)

```

### Remdesivir

```{r discharge-rem}
library(survival)
library(survminer)
adev_rem <- adev %>% filter(fas_rem == "Yes") 
fit_rem  <- surv_fit(Surv(dischargeday, dischargecens == "No") ~ rantrt, 
                      data = adev_rem)

# survdiff(Surv(dischargeday, dischargecens == "No") ~ rantrt, 
#                       data = adev_rem)

ggsurvplot(fit_rem, data = adev_rem, fun = "event", pval = TRUE)

fit_rem_28  <- surv_fit (Surv(dischargeday_28, dischargecens_28 == "No") ~ rantrt, 
                      data = adev_rem)

ggsurvplot(fit_rem_28, data = adev_rem, fun = "event", pval = TRUE)

```


# Adverse Events


## AE Summary

```{r ae-summary}

adae_fas <- adae %>% filter(fas =="Yes")

ae_summary_table <- tribble(
    ~text,  ~var, ~f,
  "Number of AEs", "anyae", "ae_N_n_pct",
  "Number of patients with any AEs?", "anyae", "ae_n_pct",
  "Number of patients with one AE", "one_ae", "ae_n_pct",
  "Number of patients with two AE", "two_ae", "ae_n_pct",
  "Number of patients with three or more AEs", "three_plus_ae", "ae_n_pct",
  "Number of SAEs", "sae", "ae_N_n_pct",
  "Number of patients with any SAEs?", "anysae","ae_n_pct"
)

tmp<-ae_summary_table %>%
  mutate(data = list(adae_fas),
         group = "rantrt",
         param = list(level = 1)) %>%
  mutate(res = pmap(list(f, data, var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  mutate(id = paste0("txt", id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, starts_with("txt")) %>%
  knitr::kable(col.names = c("Parameter", header_tot),
        caption = "Summary of Adverse Events")

tmp
```

The numbers are [Number of events] Number of patients (percentage of patients), or Number of patients (percentage of patients)


## By System Organ Class and Preferred Term

```{r aetab1}
ae_table_fns <- function(data, filtervar){

  filtervar = ensym(filtervar)

  data %>%
    group_by(rantrt) %>%
    mutate(N_pat = n_distinct(subjectid)) %>%
    filter(!!filtervar == 1)  %>%
    group_by(subjectid, rantrt, N_pat, soc_name, pt_name) %>%
    summarise(n_ae = n(),
              .groups = "drop_last") %>%
    filter(!is.na(pt_name)) %>%
    group_by(rantrt, N_pat, soc_name, pt_name) %>%
    summarise(n_pat = n(),
              n_ae = sum(n_ae),
              .groups = "drop_last") %>%
    mutate(pct = round(n_pat/N_pat*100,digits = 1),
           txt = paste0("[", n_ae,"] ", n_pat, " (", pct, "%)"),
           arm = rantrt) %>%
    ungroup %>% select(arm, soc_name, pt_name, txt) %>%
    pivot_wider(values_from = txt, names_from = arm, values_fill = list(txt = "")) %>%
    #mutate_at(vars(starts_with("arm")), ~if_else(is.na(.), "", .)) %>%
    arrange(soc_name, pt_name) %>%  group_by(soc2 = soc_name) %>%
    mutate(soc_name = if_else(row_number() != 1, "", soc_name)) %>% ungroup() %>% select(-soc2) %>%
    filter(soc_name != "NA")
}

adae_fas %>%
  bind_rows(adae_fas, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  mutate(all = 1) %>%
  ae_table_fns("all") %>%
  knitr::kable(col.names = c("System Organ Class", "Preferred Term", header_tot),
               caption = " Adverse Events by System Organ Class and Preferred term", longtable = TRUE, booktabs = TRUE) #%>%
  #column_spec(1:2, width = "5cm")
```

## Serious Adverse Events

```{r saetab}

adae_fas %>%
  bind_rows(adae, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  ae_table_fns("aesercd") %>%
  knitr::kable( col.names = c("System Organ Class", "Preferred Term", header_tot),
               caption = "Serious Adverse Events by System Organ Class and Preferred term",
         booktabs = TRUE,
         longtable = TRUE) #%>%
  #column_spec(1:2, width = "5cm")

```

## Suspected Unexpected Serious Adverse Reaction

```{r susar}

adae_fas %>%
  bind_rows(adae, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  mutate(susar = (aesercd == 1) & (saerelcd == 2) & saeexpcd ==2) %>%
  ae_table_fns("susar") %>%
  rename( "System Organ Class" = soc_name,  "Preferred Term" = pt_name) %>%
  knitr::kable(
               caption = "Suspected Unexpected Serious Adverse Reaction by System Organ Class and Preferred term",
         booktabs = TRUE,
         longtable = TRUE)

```

END