---
title: "NOR-SOLIDARITY First Interim Report"
author: "Inge Christoffer Olsen, PhD"
date: '`r format(Sys.time(), "%d %B, %Y")` '
output: word_document
params:
  viedoc_export: ous_20201016_084109
  pseudorandom: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(ggformula)
library(wesanderson)
library(rlang)
library(glue)
library(knitr)
library(labelled)
library(survival)
library(survminer)

```

```{r load-datasets, include = FALSE}

tddm <- read_rds("data/td/tddm.rds")
tdran <- read_rds("data/td/tdran.rds")
raw <- read_rds("data/raw/raw.rds")
adsl <- read_rds("data/ad/adsl.rds")
adex <- read_rds("data/ad/adex.rds")
adeff <- read_rds("data/ad/adeff.rds")
adae <- read_rds("data/ad/adae.rds")
tdex <- read_rds("data/td/tdex.rds")
addm <- read_rds("data/ad/addm.rds")
adev <- read_rds("data/ad/adev.rds")


source("src/External/functions.R", local = knitr::knit_global())
export_date = substr(params$viedoc_export,5,19) %>% lubridate::as_datetime()
if(params$pseudorandom) {
  pr_text = "While the results are based on real data, the treatment allocation has been drawn randomly for this report. Thus, this is a mock-up report intended to show how the final report will look like, without showing the actual results of the trial and the treatment differences."
} else {
  pr_text = "The results in this report is according to the true random allocation. "
}
```


# Introduction
This is the report for the first interim analysis of the NOR-SOLIDARITY trial. The data are based on an export from the Viedoc electronic data capture at "`r export_date`" system time stamped "`r params$viedoc_export`". `r pr_text` There were `r n_distinct(adsl)` included patients.

# Inclusion status

## Inclusion rate


```{r inclusionplot, echo = FALSE}
adsl %>% 
  filter(fas == "Yes") %>% 
  arrange(randt) %>% 
  mutate(n = row_number()) %>% 
  gf_line(n ~ randt, color = wes_palette(n=1, name = "Darjeeling1")) %>% 
  gf_theme(theme = theme_classic()) %>% 
  gf_labs(y = "Number randomised", x = "Date")
```

## Inclusion by hospital

```{r by-site, echo = FALSE}


adsl %>% 
  filter(fas == "Yes") %>% 
  group_by(sitename) %>% 
  mutate(n=n()) %>% 
  arrange(-n) %>%  
  gf_bar(~ reorder(sitename, -n), fill = wes_palette(n=1, name = "Darjeeling1")) %>% 
  gf_theme(theme = theme_classic() ) %>% 
  gf_theme(axis.text.x = element_text(angle = 45, hjust = 1)) %>% 
  gf_labs(x = "", y = "Number randomised")

```

## By treatment

```{r by-treatment, echo = FALSE}



adsl %>% 
  filter(fas == "Yes") %>% 
  group_by(rantrt) %>% 
  summarise(n=n(), .groups = "drop_last") %>% 
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")) +
  theme_classic() + 
  theme(legend.position = "none") + 
  labs(x="", y = "Number randomised (all) in FAS")

adsl %>% 
  filter(fas_hcq == "Yes") %>% 
  group_by(rantrt) %>% 
  summarise(n=n(), .groups = "drop_last") %>% 
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")) +
  theme_classic() + 
  theme(legend.position = "none") + 
  labs(x="", y = "Number randomised (HCQ available) in FAS")


adsl %>% 
  filter(fas_rem == "Yes") %>% 
  group_by(rantrt) %>% 
  summarise(n=n(), .groups = "drop_last") %>% 
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")[c(1,3)]) +
  theme_classic() + 
  theme(legend.position = "none") + 
  labs(x="", y = "Number randomised (remdesivir available) in FAS")




```

\newpage



```{r headers}
arms_tot <- c("SOC", "SOC + HCQ", "SOC + Remdesivir")
total_n <- n_distinct(adsl$subjectid)

arms_hcq <- arms_tot[c(1,2)]
arms_rem <- arms_tot[c(1,3)]

header <- function(data, arms){

 data %>%
  group_by(rantrt, subjectid) %>%
  summarise(n=n(), .groups = "drop_last") %>%
  group_by(rantrt) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  ungroup() %>%
  mutate(armtxt = arms) %>%
  mutate(txt = paste0(armtxt, " (N=", n, ")")) %>%
  select(txt) %>%
  deframe
}

header_tot <- adsl %>% 
  filter(fas=="Yes") %>% 
  header(arms_tot)

header_hcq <- adsl %>% 
  filter(fas_hcq=="Yes") %>% 
  header(arms_hcq)

header_rem <- adsl %>% 
  filter(fas_rem=="Yes") %>% 
  header(arms_rem)

```


#Patient flow

```{r patient-flow}
fas_table <- tribble(
  ~text, ~f, ~var, ~param,   
  "Enrolled", "n_pct", "enrolled", list(level = "Yes"),
  "Randomised", "n_pct", "randomised", list(level = "Yes"), 
  "Included in FAS", "n_pct", "fas", list(level = "Yes"),
  "Excluded from FAS, No post-randomisation information", "n_pct", "fasex1", list(level = "Yes"),
  "Excluded from FAS, incorrect inclusion", "n_pct", "fasex2", list(level = "Yes")
  )

fas_table %>% 
  mutate(data = list(adsl %>% mutate(tmp = "Enrolled")),
         group = "tmp") %>% 
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>% 
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, Enrolled) %>% 
  knitr::kable(col.names = c("Parameter", "Total"),
               caption = "Patient flow total")

fas_table %>% 
  filter(text != "Enrolled") %>% 
  mutate(data = list(adsl),
         group = "rantrt") %>% 
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>% 
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, any_of(levels(adsl$rantrt))) %>% 
  knitr::kable(col.names = c("Parameter", arms_tot),
               caption = "Patient flow by arm")
```


# Demographics




```{r demographics, warning = FALSE, message = FALSE, results = 'asis', echo = FALSE}

dm_table <- tribble(
  ~text, ~f, ~var, ~param,
  "Age (years)", "mean_sd", "age_calc", list(digits = 1), 
  "Female, n (%)", "n_pct", "sex", list(level = "Female"), 
  "Admitted to ward, n(%)", "n_pct", "sq_admis", list(level = "Ward"),
  "Admitted to ICU, n(%)", "n_pct", "sq_admis", list(level = "ICU"),
  "WHO Moderate disease state (4-5), n(%)", "n_pct", "rcwhostate", list(level = "Moderate"),
  "WHO Severe disease state (6-9), n(%)", "n_pct", "rcwhostate", list(level = "Severe"),
  "WHO Severe disease state (6), n(%)", "n_pct", "rcwhocps", list(level = 6),  
  "Body Mass Index (kg/m^2^) mean", "mean_sd", "vsbmi", list(digits = 0),
  "Body Mass Index (kg/m^2^) median", "median_iqr", "vsbmi", list(digits = 0),
  "Obese (BMI > 30 kg/m^2^), n(%)", "n_pct", "vsobese", list(level="Obese"),
  "Systolic Blood Pressure (mmHg)", "mean_sd", "vssys", list(digits = 0),
  "Diastolic Blood Pressure (mmHg)", "mean_sd", "vsdia", list(digits = 0), 
  "Mean Arterial Blood Pressure (mmHg)", "mean_sd", "vsmap", list(digits = 0),
  "Temperature (°C)", "mean_sd", "vstemp", list(digits = 1), 
  "SOFA score", "mean_sd", "scsumsc", list(digits = 1),
  "**Comorbidities or risk factors**", "empty", "", list(),
  " Chronic cardiac disease, including congenital heart disease", "n_pct", "cc_card", list(level = "Yes"),
  " Ever smoking, n(%)", "n_pct", "cc_eversmoker", list(level = "Yes"), 
  " Hypertension, n(%)", "n_pct", "cc_ht", list(level = "Yes"),
  " Chronic pulmonary disease, n(%)", "n_pct", "cc_copd", list(level = "Yes"),
  " Chronic kidney disease, n(%)", "n_pct", "cc_ckd", list(level = "Yes"),
  " Autoimmune disease, n(%)", "n_pct", "cc_aid", list(level = "Yes"),
  " Diabetes, n(%)", "n_pct", "cc_diab", list(level = "Yes"),
  " Cognitive impairment/dementia, n(%)", "n_pct", "cc_cogn", list(level = "Yes"),
  " Neurological disorder, n(%)", "n_pct", "cc_neur", list(level = "Yes"),
  " Cancer, n(%)", "n_pct", "cc_cance", list(level = "Yes"),
  " Cirrhosis, n(%)", "n_pct", "cc_cirr", list(level = "Yes"),
  " Asthma, n(%)", "n_pct", "cc_asthm", list(level = "Yes"),
  " HIV, n(%)", "n_pct", "cc_hiv", list(level = "Yes"),
  " Active TB, n(%)", "n_pct", "cc_tb", list(level = "Yes"),
  "**Co-medications**", "empty", "", list(),
  "Steroids", "n_pct", "me9", list(level = "Yes"),
  "Other immunomodulatory drugs", "n_pct", "me10", list(level = "Yes"),
  "ACE inhibitor", "n_pct", "me1", list(level = "Yes"),
  "AT-II blockers", "n_pct", "me2", list(level = "Yes")
)

labtable <- addm %>% 
  select(lbferres:lbwbcres) %>% 
  var_label(unlist = TRUE)  
  
labtable <- tibble(text = labtable, 
                   var = names(labtable),
                   f = "median_iqr",
                   param = list(tibble(digits = 1)))   

dm_table <- dm_table %>%
  add_row(tibble_row(text ="Median Laboratory values (IQR)", 
                     f = "empty", var = "")) %>% 
  add_row(labtable)
  
  

dm_table_f <- function( data, table_temp, caption, header){
table_temp %>%
  mutate(data = list(data),
         group = "rantrt") %>%
  mutate(res = pmap(list(f, data, var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, any_of(levels(adsl$rantrt))) %>%
  knitr::kable(col.names = c("Parameter", header),
               caption = caption)
}


addm_hcq <- addm  %>% filter(fas_hcq == "Yes")
addm_rem <- addm  %>% filter(fas_rem == "Yes")


dm_table_f(addm, dm_table, "Demographics, all arms (FAS)", header_tot)

dm_table_f(addm_hcq, dm_table, "Demographics, HCQ (FAS)", header_hcq)

dm_table_f(addm_rem, dm_table, "Demographics, Remdesivir (FAS)", header_rem)


missing_table <- dm_table %>% 
  mutate(f = if_else(var == "", "empty","missing_f")) 

dm_table_f(addm, missing_table, "Missing values, all arms (FAS)", header_tot)


```

# Exposure

```{r exposure, results = "asis", echo = FALSE}

ex_table <- tribble(
  ~text, ~f, ~var, ~param,   
  "Total dose (mg), median (IQR)", "median_iqr", "extotdose", list(digits = 0),
  "Treatment duration, median (IQR)", "median_iqr", "extrtdur", list(digits = 0), 
  "Number of doses given, median (IQR)", "median_iqr", "exndose", list(digits = 0),
  "Patients with any treatment discrepencies, n (%)	", "n_pct", "exdisc", list(level = "Yes")
  )

ex_table %>% 
  mutate(data = list(adex %>% filter(fas == "Yes")),
         group = "rantrt") %>% 
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>% 
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, c("Hydroxychloroquine + SOC", "Remdesivir + SOC")) %>% 
  knitr::kable(col.names = c("Parameter", header_tot[c(2,3)]),
               caption = "Exposure to study treatment")






```
# Efficacy

## Mortality

### Descriptives
```{r mortality-descriptives}

mort_desc_f <- function(filter_name = fas, caption){
adev %>% filter({{filter_name}} == "Yes") %>% 
  group_by(rantrt, survcens) %>% 
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(N =  sum(n),
         pct = round(n/N*100, digits = 1)) %>% 
  filter(survcens =="No") %>% 
  select(-survcens) %>% 
  knitr::kable(col.names = c("Treatment", "# deaths", "# randomised", "%"), caption = caption)
}

mort_desc_f(caption = "All arms (FAS)")

mort_desc_f(fas_hcq, caption = "HCQ (FAS)")

mort_desc_f(fas_rem, caption = "Remdesivir (FAS)")


```

```{r mortres}
mortres <- read_rds("results/rds/mortres.rds")



mortres %>% 
  mutate(title = glue::glue("{fname}, {dname}"),
         plot = map2(plot, title, ~ .x + ggtitle(.y)),
         walk(plot,print)) %>% 
  invisible()
  
mortres %>% 
   mutate(title = glue::glue("{fname}, {dname}")) %>% 
  select(title, RR, pval) %>% 
  knitr::kable(caption = "Relative risk estimates and p-values",
               col.names = c("Timeframe, Population", "Relative risk", "P-value"))


```



```{r efflbres, results = "asis", echo = FALSE}
efflbres <- read_rds("results/rds/efflbres2.rds")



plot_cont_margins <- function(data, ytitle = "Value") {
  data %>%
    gf_line(
      margin ~ studyday,
      color = ~ rantrt,
      group = ~ rantrt,
      position = position_dodge(0.4),
      size = 1
    ) %>%
    gf_point(position = position_dodge(0.4)) %>%
    gf_errorbar(
      ci_lb + ci_ub ~ studyday,
      color = ~ rantrt,
      width = .8,
      position = position_dodge(0.4)
    ) %>%
    gf_labs(x = "Study day",
            y = ytitle,
            color = "Treatment") %>%
    gf_theme(theme_classic())
    
}


efflbres <- efflbres %>% 
  mutate(marginsplot = pmap(list(data = margins, ytitle = label), plot_cont_margins),
         title = glue::glue("{label}, {population}"))

efflbres %>% 
  mutate(walk2(descriptives, title, ~knitr::kable(.x, caption = .y) %>% print),
         desc_plot2 = map2(desc_plot, title, ~ .x + ggtitle(.y)),
         walk(desc_plot2, print),
         walk(marginsplot, print),
         walk2(diffs, title,  ~knitr::kable(.x, caption = .y, 
                                            col.names = c("Treatment", 
                                                          "Days since randomisation", 
                                                          "Treatment difference",
                                                          "P-value", 
                                                          "Lower 95% CL",
                                                          "Upper 95% CL")) %>% 
                 print)
         )  %>% 
  invisible()
  


```


# Adverse Events


## AE Summary

```{r ae-summary}

adae_fas <- adae %>% filter(fas =="Yes")

ae_summary_table <- tribble(
    ~text,  ~var, ~f,
  "Number of AEs", "anyae", "ae_N_n_pct",
  "Number of patients with any AEs?", "anyae", "ae_n_pct",
  "Number of patients with one AE", "one_ae", "ae_n_pct",
  "Number of patients with two AE", "two_ae", "ae_n_pct",
  "Number of patients with three or more AEs", "three_plus_ae", "ae_n_pct",
  "Number of SAEs", "sae", "ae_N_n_pct",
  "Number of patients with any SAEs?", "anysae","ae_n_pct"
)

tmp<-ae_summary_table %>%
  mutate(data = list(adae_fas),
         group = "rantrt",
         param = list(level = 1)) %>%
  mutate(res = pmap(list(f, data, var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  mutate(id = paste0("txt", id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, starts_with("txt")) %>%
  knitr::kable(col.names = c("Parameter", header_tot),
        caption = "Summary of Adverse Events")

tmp
```

The numbers are [Number of events] Number of patients (percentage of patients), or Number of patients (percentage of patients)


## By System Organ Class and Preferred Term

```{r aetab1}
ae_table_fns <- function(data, filtervar){

  filtervar = ensym(filtervar)

  data %>%
    group_by(rantrt) %>%
    mutate(N_pat = n_distinct(subjectid)) %>%
    filter(!!filtervar == 1)  %>%
    group_by(subjectid, rantrt, N_pat, soc_name, pt_name) %>%
    summarise(n_ae = n(),
              .groups = "drop_last") %>%
    filter(!is.na(pt_name)) %>%
    group_by(rantrt, N_pat, soc_name, pt_name) %>%
    summarise(n_pat = n(),
              n_ae = sum(n_ae),
              .groups = "drop_last") %>%
    mutate(pct = round(n_pat/N_pat*100,digits = 1),
           txt = paste0("[", n_ae,"] ", n_pat, " (", pct, "%)"),
           arm = rantrt) %>%
    ungroup %>% select(arm, soc_name, pt_name, txt) %>%
    pivot_wider(values_from = txt, names_from = arm, values_fill = list(txt = "")) %>%
    #mutate_at(vars(starts_with("arm")), ~if_else(is.na(.), "", .)) %>%
    arrange(soc_name, pt_name) %>%  group_by(soc2 = soc_name) %>%
    mutate(soc_name = if_else(row_number() != 1, "", soc_name)) %>% ungroup() %>% select(-soc2) %>%
    filter(soc_name != "NA")
}

adae_fas %>%
  bind_rows(adae_fas, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  mutate(all = 1) %>%
  ae_table_fns("all") %>%
  knitr::kable(col.names = c("System Organ Class", "Preferred Term", header_tot),
               caption = " Adverse Events by System Organ Class and Preferred term", longtable = TRUE, booktabs = TRUE) #%>%
  #column_spec(1:2, width = "5cm")
```

## Serious Adverse Events

```{r saetab}

adae_fas %>%
  bind_rows(adae, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  ae_table_fns("aesercd") %>%
  knitr::kable( col.names = c("System Organ Class", "Preferred Term", header_tot),
               caption = "Serious Adverse Events by System Organ Class and Preferred term",
         booktabs = TRUE,
         longtable = TRUE) #%>%
  #column_spec(1:2, width = "5cm")

```

## Suspected Unexpected Serious Adverse Reaction

```{r susar}

adae_fas %>%
  bind_rows(adae, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  mutate(susar = (aesercd == 1) & (saerelcd == 2) & saeexpcd ==2) %>%
  ae_table_fns("susar") %>%
  rename( "System Organ Class" = soc_name,  "Preferred Term" = pt_name) %>%
  knitr::kable(
               caption = "Suspected Unexpected Serious Adverse Reaction by System Organ Class and Preferred term",
         booktabs = TRUE,
         longtable = TRUE)

```

<!-- # Mortality and other outcomes by admission state -->

<!-- ```{r} -->
<!-- adeff %>% -->
<!--   group_by(sq_admis, outcome) %>% -->
<!--   summarise(n = n(), .groups = "drop_last") %>% -->
<!--   group_by(sq_admis) %>% -->
<!--   mutate(tot = sum(n), -->
<!--            pct = round(n/tot*100,digits = 1)) %>% -->
<!--   mutate(txt = paste0(n, " (", pct, "%)")) %>% -->
<!--   ungroup %>% -->
<!--   select(-(n:pct)) %>% -->
<!--   pivot_wider(values_from = txt, names_from = sq_admis) %>% -->
<!--   knitr::kable( booktabs = TRUE, caption = "Outcome") -->

<!-- ``` -->




<!-- # Outcome -->

<!-- The following report is based on pseudo-randomised groups, not true allocations. The true allocations are available for the DMC only. -->

<!-- ```{r outcome} -->

<!-- adeff %>% -->
<!--   mutate(rantrt = sample(rantrt, n(), replace = FALSE)) %>% #Delete this row for true allocations -->
<!--   group_by(rantrt, outcome) %>% -->
<!--   summarise(n = n(), .groups = "drop_last") %>% -->
<!--   group_by(rantrt) %>% -->
<!--   mutate(tot = sum(n), -->
<!--            pct = round(n/tot*100,digits = 1)) %>% -->
<!--   mutate(txt = paste0(n, " (", pct, "%)")) %>% -->
<!--   ungroup %>% -->
<!--   select(-(n:pct)) %>% -->
<!--   pivot_wider(values_from = txt, names_from = rantrt) %>% -->
<!--   knitr::kable(col.names = c("Parameter", header), booktabs = TRUE, caption = "Outcome") -->


<!-- ``` -->

