---
title: "NOR-SOLIDARITY First Interim Report"
author: "Inge Christoffer Olsen, PhD"
date: '`r format(Sys.time(), "%d %B, %Y")` '
output: word_document
params:
  viedoc_export: ous_20201016_084109
  pseudorandom: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(ggformula)
library(wesanderson)
library(rlang)
library(glue)
library(knitr)
library(labelled)
library(survival)
library(survminer)

```

```{r load-datasets, include = FALSE}

tddm <- read_rds("data/td/tddm.rds")
tdran <- read_rds("data/td/tdran.rds")
raw <- read_rds("data/raw/raw.rds")
adsl <- read_rds("data/ad/adsl.rds")
adex <- read_rds("data/ad/adex.rds")
adeff <- read_rds("data/ad/adeff.rds")
adae <- read_rds("data/ad/adae.rds")
tdex <- read_rds("data/td/tdex.rds")
addm <- read_rds("data/ad/addm.rds")
adev <- read_rds("data/ad/adev.rds")
tdds <- read_rds("data/td/tdds.rds")

source("src/External/functions.R", local = knitr::knit_global())
export_date = substr(params$viedoc_export,5,19) %>% lubridate::as_datetime()
if(params$pseudorandom) {
  pr_text = "While the results are based on real data, the treatment allocation has been drawn randomly for this report. Thus, this is a mock-up report intended to show how the final report will look like, without showing the actual results of the trial and the treatment differences."
} else {
  pr_text = "The results in this report is according to the true random allocation. "
}
```


# Introduction
This is the report for the first interim analysis of the NOR-SOLIDARITY trial. The data are based on an export from the Viedoc electronic data capture at "`r export_date`" system time stamped "`r params$viedoc_export`". `r pr_text` There were `r n_distinct(adsl)` included patients.

# Inclusion status

## Inclusion rate


```{r inclusionplot, echo = FALSE}
adsl %>%
  filter(fas == "Yes") %>%
  arrange(randt) %>%
  mutate(n = row_number()) %>%
  gf_line(n ~ randt, color = wes_palette(n=1, name = "Darjeeling1")) %>%
  gf_theme(theme = theme_classic()) %>%
  gf_labs(y = "Number randomised", x = "Date")
```

## Inclusion by hospital

```{r by-site, echo = FALSE}


adsl %>%
  filter(fas == "Yes") %>%
  group_by(sitename) %>%
  mutate(n=n()) %>%
  arrange(-n) %>%
  gf_bar(~ reorder(sitename, -n), fill = wes_palette(n=1, name = "Darjeeling1")) %>%
  gf_theme(theme = theme_classic() ) %>%
  gf_theme(axis.text.x = element_text(angle = 45, hjust = 1)) %>%
  gf_labs(x = "", y = "Number randomised")

```

## By treatment

```{r by-treatment, echo = FALSE}



adsl %>%
  filter(fas == "Yes") %>%
  group_by(rantrt) %>%
  summarise(n=n(), .groups = "drop_last") %>%
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(x="", y = "Number randomised (all) in FAS")

adsl %>%
  filter(fas_hcq == "Yes") %>%
  group_by(rantrt) %>%
  summarise(n=n(), .groups = "drop_last") %>%
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(x="", y = "Number randomised (HCQ available) in FAS")


adsl %>%
  filter(fas_rem == "Yes") %>%
  group_by(rantrt) %>%
  summarise(n=n(), .groups = "drop_last") %>%
ggplot(data=., aes(x = rantrt, y = n, fill = rantrt)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=n), vjust=1.6, color="white",
            position = position_dodge(0.9), size=3.5) +
  scale_fill_manual(values=wes_palette(n=3, name="Darjeeling1")[c(1,3)]) +
  theme_classic() +
  theme(legend.position = "none") +
  labs(x="", y = "Number randomised (remdesivir available) in FAS")




```



```{r headers}
arms_tot <- c("SOC", "SOC + HCQ", "SOC + Remdesivir")
total_n <- n_distinct(adsl$subjectid)

arms_hcq <- arms_tot[c(1,2)]
arms_rem <- arms_tot[c(1,3)]
arms_all <- "All patients"

header <- function(data, arms){

 data %>%
  group_by(rantrt, subjectid) %>%
  summarise(n=n(), .groups = "drop_last") %>%
  group_by(rantrt) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  ungroup() %>%
  mutate(armtxt = arms) %>%
  mutate(txt = paste0(armtxt, " (N=", n, ")")) %>%
  select(txt) %>%
  deframe
}

header_tot <- adsl %>%
  filter(fas=="Yes") %>%
  header(arms_tot)

header_hcq <- adsl %>%
  filter(fas_hcq=="Yes") %>%
  header(arms_hcq)

header_rem <- adsl %>%
  filter(fas_rem=="Yes") %>%
  header(arms_rem)

header_all <- adsl %>% 
  filter(fas == "Yes") %>% 
  summarise(n=n(), .groups = "drop_last") %>% 
  mutate(txt = paste0("All patients (N=", n, ")")) %>% 
  select(txt) %>% 
  deframe

```


# Patient flow

```{r patient-flow}

adsl_all <- readr::read_rds("data/ad/adsl_all.rds")

fas_table <- tribble(
  ~text, ~f, ~var, ~param,
  "Enrolled", "n_pct", "enrolled", list(level = "Yes"),
  "Randomised", "n_pct", "randomised", list(level = "Yes"),
  "Included in FAS", "n_pct", "fas", list(level = "Yes"),
  "Excluded from FAS, No post-randomisation information", "n_pct", "fasex1", list(level = "Yes"),
  "Excluded from FAS, incorrect inclusion", "n_pct", "fasex2", list(level = "Yes")
  )

fas_table %>%
  mutate(data = list(adsl_all %>% mutate(tmp = "Enrolled")),
         group = "tmp") %>%
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, Enrolled) %>%
  knitr::kable(col.names = c("Parameter", "Total"),
               caption = "Patient flow total")

fas_table %>%
  filter(text != "Enrolled") %>%
  mutate(data = list(adsl_all),
         group = "rantrt") %>%
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, any_of(levels(adsl$rantrt))) %>%
  knitr::kable(col.names = c("Parameter", arms_tot),
               caption = "Patient flow by arm")

adsl %>% 
  left_join(tdds, by = "subjectid") %>% 
  group_by(eosreas, rantrt) %>% 
  summarise(n = n(), .groups = "drop_last") %>% 
  pivot_wider(names_from = rantrt, values_from = n) %>% 
  mutate(across(where(is.integer), ~ if_else(is.na(.x), 0L, .x))) %>% 
  mutate(eosreas = str_trunc(as.character(eosreas), 40, ellipsis = ""),
         Total = `Standard of care (SOC)` + `Hydroxychloroquine + SOC` + `Remdesivir + SOC`) %>% 
  mutate(eosreas = if_else(is.na(eosreas), "Completed", eosreas)) %>% 
  rename(Reason = eosreas ) %>% 
  knitr::kable(caption = "Patient flow during study (FAS)")
  

```


# Demographics


```{r demographics, warning = FALSE, message = FALSE, results = 'asis', echo = FALSE}

dm_table <- tribble(
  ~text, ~f, ~var, ~param,
  "**Demographics**", "empty", "", list(),
  "  Age (years)", "mean_sd", "age_calc", list(digits = 1),
  "  Female, n (%)", "n_pct", "sex", list(level = "Female"),
  "  Body Mass Index (kg/m^2^)", "mean_sd", "vsbmi", list(digits = 0),
  "  Body Mass Index (kg/m^2^)", "median_iqr", "vsbmi", list(digits = 0),
  "  Symptoms prior to admission (days)", "mean_sd", "sympdur", list(digits = 1),
  "  P/F-ratio at admittance (kPa)", "mean_sd", "rcratio", list(digits = 0),
  "  P/F-ratio < 40kPa, n (%)", "n_pct", "rcratio40", list(level = "Yes"),
  "  Temperature (°C)", "mean_sd", "vstemp", list(digits = 1),
  "  Admitted to ward, n(%)", "n_pct", "sq_admis", list(level = "Ward"),
  "  Admitted to ICU, n(%)", "n_pct", "sq_admis", list(level = "ICU"),
  " WHO Moderate disease state (4-5), n(%)", "n_pct", "rcwhostate", list(level = "Moderate"),
  "  WHO Severe disease state (6-9), n(%)", "n_pct", "rcwhostate", list(level = "Severe"),
  "  WHO Severe disease state (6), n(%)", "n_pct", "rcwhocps", list(level = 6),
  "  WHO Severe disease state (5), n(%)", "n_pct", "rcwhocps", list(level = 5),
    "**Comorbidities**", "empty", "", list(),
  "  Chronic cardiac disease, including congenital heart disease", "n_pct", "cc_card", list(level = "Yes"),
  "  Chronic pulmonary disease, n(%)", "n_pct", "cc_copd", list(level = "Yes"),
  "  Ever smoking, n(%)", "n_pct", "cc_eversmoker", list(level = "Yes"),
  "  Hypertension, n(%)", "n_pct", "cc_ht", list(level = "Yes"),
  "  Diabetes, n(%)", "n_pct", "cc_diab", list(level = "Yes"),
  "  Obese (BMI > 30 kg/m^2^), n(%)", "n_pct", "vsobese", list(level="Obese"),
  "**Co-medications**", "empty", "", list(),
  "  Steroids", "n_pct", "me9", list(level = "Yes"),
  "  Other immunomodulatory drugs", "n_pct", "me10", list(level = "Yes"),
  "  ACE inhibitor", "n_pct", "me1", list(level = "Yes"),
  "  AT-II blockers", "n_pct", "me2", list(level = "Yes"),
  "**Hematology**", "empty", "", list(),
  "  Hemoglobin (g/dL)", "median_iqr", "lbhbres", list(digits = 1),
  "  WBC (x10^9^/L)", "median_iqr", "lbwbcres", list(digits = 1),
  "  Neutrophils (x10^9^/L)", "median_iqr", "lbneures", list(digits = 1),
  "  Lymphocytes (x10^9^/L)", "median_iqr", "lblymres", list(digits = 1),
  "  Platelet counts (x10^9/L)", "median_iqr", "lbpcres", list(digits = 1),
  "**Inflammatory markers**", "empty", "", list(),
  "  CRP (mg/L)", "median_iqr", "lbcrpres", list(digits = 1),
  "  Procalcitonin (µg/L)", "median_iqr", "lbprores", list(digits = 2),
  "  Ferritin (µg/L)", "median_iqr", "lbferres", list(digits = 1),
  "**Other**", "empty", "", list(),
  "  LDH (U/L)", "median_iqr", "lbldres", list(digits = 1),
  "  D-dimer (mg/L FEU)", "median_iqr", "lbdimres1", list(digits = 2),
  "  AST ", "median_iqr", "lbastres", list(digits = 1),
  "  ALT ", "median_iqr", "lbaltres", list(digits = 1),
  "  eGFR (mL/min/1.73 m^2^) ", "median_iqr", "lbegfrc", list(digits = 1),
  "**Viral count**", "empty", "", list(),
  "  Viral count (log~10~ counts/1000 cells)", "mean_sd", "vllog10cpkc", list(digits = 1),
  "**Anti-SARS-CoV-2 Antibodies**", "empty", "", list(),
  "  Zero converted (RBD ≤ 5)", "n_pct", "abzeroc", list(level = "Yes"),
  "**Supplementary baseline information**", "empty", "", list(),
  "  Systolic Blood Pressure (mmHg)", "mean_sd", "vssys", list(digits = 0),
  "  Diastolic Blood Pressure (mmHg)", "mean_sd", "vsdia", list(digits = 0),
  "  Mean Arterial Blood Pressure (mmHg)", "mean_sd", "vsmap", list(digits = 0),
  "  SOFA score", "mean_sd", "scsumsc", list(digits = 1),
  "  Chronic kidney disease, n(%)", "n_pct", "cc_ckd", list(level = "Yes"),
  "  Autoimmune disease, n(%)", "n_pct", "cc_aid", list(level = "Yes"),
  "  Cognitive impairment/dementia, n(%)", "n_pct", "cc_cogn", list(level = "Yes"),
  "  Neurological disorder, n(%)", "n_pct", "cc_neur", list(level = "Yes"),
  "  Cancer, n(%)", "n_pct", "cc_cance", list(level = "Yes"),
  "  Cirrhosis, n(%)", "n_pct", "cc_cirr", list(level = "Yes"),
  "  Asthma, n(%)", "n_pct", "cc_asthm", list(level = "Yes"),
  "  HIV, n(%)", "n_pct", "cc_hiv", list(level = "Yes"),
  "  Active TB, n(%)", "n_pct", "cc_tb", list(level = "Yes"),
  "Note, all percentages are given with observed values in the denominator, missing values discarded   ", "empty", "", list()
)



dm_table_f <- function(data, table_temp, caption, header, group = "rantrt"){
table_temp %>%
  mutate(data = list(data),
         group = group) %>%
  mutate(res = pmap(list(f, data, var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, any_of(levels(adsl$rantrt)), any_of("Yes")) %>%
  knitr::kable(col.names = c("Parameter", header),
               caption = caption)
}


addm_hcq <- addm  %>% filter(fas_hcq == "Yes")
addm_rem <- addm  %>% filter(fas_rem == "Yes")

dm_table_f(addm, dm_table, "Demographics, all patients (FAS)", header_all, group = "fas")

dm_table_f(addm, dm_table, "Demographics, all arms (FAS)", header_tot)

dm_table_f(addm_hcq, dm_table, "Demographics, HCQ (FAS)", header_hcq)

dm_table_f(addm_rem, dm_table, "Demographics, Remdesivir (FAS)", header_rem)


missing_table <- dm_table %>%
  mutate(f = if_else(var == "", "empty","missing_f"))

dm_table_f(addm, missing_table, "Missing values, all arms (FAS)", header_tot)


```

# Exposure

```{r exposure, results = "asis", echo = FALSE}

ex_table <- tribble(
  ~text, ~f, ~var, ~param,
  "Total dose (mg), median (IQR)", "median_iqr", "extotdose", list(digits = 0),
  "Treatment duration, median (IQR)", "median_iqr", "extrtdur", list(digits = 0),
  "Number of doses given, median (IQR)", "median_iqr", "exndose", list(digits = 0),
  "Patients with any treatment discrepencies, n (%)	", "n_pct", "exdisc", list(level = "Yes")
  )

ex_table %>%
  mutate(data = list(adex %>% filter(fas == "Yes")),
         group = "rantrt") %>%
  mutate(res = pmap(list(f, data , var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, c("Hydroxychloroquine + SOC", "Remdesivir + SOC")) %>%
  knitr::kable(col.names = c("Parameter", header_tot[c(2,3)]),
               caption = "Exposure to study treatment")






```
# Efficacy

## Mortality

### Descriptives
```{r mortality-descriptives}



mort_desc_f <- function(filter_name = fas, caption){
adev %>% filter({{filter_name}} == "Yes") %>%
  group_by(rantrt, survcens) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(N =  sum(n),
         pct = round(n/N*100, digits = 1)) %>%
  filter(survcens =="No") %>%
  select(-survcens) %>%
  knitr::kable(col.names = c("Treatment", "# deaths", "# randomised", "%"), caption = caption)
}

mort_desc_f(caption = "All arms (FAS)")

mort_desc_f(fas_hcq, caption = "HCQ (FAS)")

mort_desc_f(fas_rem, caption = "Remdesivir (FAS)")


```
## Mortality Estimates
```{r mortres, results = "asis"}
rdev <- read_rds("results/rds/rdev.rds")



rdev %>%
  mutate(title = glue::glue("{fname}, {dname}"),
         plot = map2(plot, title, ~ .x + ggtitle(.y)),
         walk(plot,print)) %>%
  invisible()

rdev %>%
   mutate(title = glue::glue("{fname}, {dname}")) %>%
  select(title, RR, pval) %>%
  knitr::kable(caption = "Relative risk estimates and p-values",
               col.names = c("Timeframe, Population", "Relative risk", "P-value"))


```
# Viral load

```{r viral-load, results = "asis"}
adsl <- readr::read_rds("data/ad/adsl.rds")
tdvl<- readr::read_rds("data/td/tdvl.rds")

source("src/make_rd/stata.R")

rdlv_margins <- function(data = advl,
                           var = "vllog10cpkc_imp",
                           population = "fas") {
  var_ <- ensym(var)
  population <- ensym(population)
  
  data <- data %>%
    filter(!!population == "Yes" &
             studyday %in% c(-3:15) &
             vlsource %in% c("Labfile only", "Both")) %>%
    mutate(rantrt = fct_drop(rantrt),
           marginset = if_else(studyday %in% c(0, 4 , 8, 15), studyday, NA_real_)) 
  
  x <- glue::glue(
    "
    
mkspline time_1 4 time_2 8 time_3 = studyday
mkspline time1 7 time2  = studyday

tempfile tmp1
tempfile tmp2
tempfile tmp3

mixed {var} i.rantrt##c.(time_1 time_2 time_3)  || subjectid: studyday, covariance(unstructured)
margins i.rantrt, over(marginset) saving(`tmp1')

mixed {var} i.rantrt##c.(time1 time2)  || subjectid: studyday, covariance(unstructured)
margins i.rantrt, dydx(time1) saving(`tmp2')
margins r.rantrt, dydx(time1) saving(`tmp3')

use `tmp1', clear
append using `tmp2' `tmp3' , gen(analysis)

"
  )
  
  margins <-  stata(
    src = x,
    data.in = data,
    data.out = TRUE,
    stata.path = "/usr/local/bin/stata-se",
    stata.version = 16,
    stata.echo = FALSE
  )
  
  res <- margins %>%
    rename_all(~ str_replace(., "_", "")) %>%
    select(rantrt = m1 , studyday = by1, margin, ci_lb, ci_ub, pvalue, analysis) 

  
  return(res)
  
}



plot_cont_margins <- function(data, ytitle = "Value") {
  data %>%
    gf_line(
      margin ~ studyday,
      color = ~ rantrt,
      group = ~ rantrt,
      position = position_dodge(0.4),
      size = 1
    ) %>%
    gf_point(position = position_dodge(0.4)) %>%
    gf_errorbar(
      ci_lb + ci_ub ~ studyday,
      color = ~ rantrt,
      width = .8,
      position = position_dodge(0.4)
    ) %>%
    gf_labs(x = "Study day",
            y = str2expression(ytitle),
            color = "Treatment") %>%
    gf_theme(theme_classic())

}



advl <- adsl %>% 
  left_join(tdvl, by = c("subjectid")) %>% 
  mutate(vllog10cpkc_imp = if_else(vldetect == "Detected", vllog10cpkc, 0)) 


rdlv_margins(population = "fas_rem") %>% 
  filter(analysis == 0) %>% 
  plot_cont_margins(ytitle = "Viral~load~(log[10]~copies~per~1000~cells)") 
  

rdlv_margins(population = "fas_rem") %>% 
  filter(analysis != 0) %>% 
  mutate(Explanation = if_else(analysis == 1, "Slope by treatment", "Difference in slope")) %>% 
  select(-analysis) %>%
  select(rantrt, Explanation, margin, ci_lb, ci_ub, pvalue) %>% 
  knitr::kable(col.names = c("Treatment",
                             "Explanation",
                              "Estimate",
                              "Lower 95% CL",
                              "Upper 95% CL",
                              "P-value"),
               digits = 3, caption = "Estimated treatment effect, Remdesivir")

rdlv_margins(population = "fas_hcq") %>% 
  filter(analysis == 0) %>% 
  plot_cont_margins(ytitle = "Viral~load~(log[10]~copies~per~1000~cells)") 
  

rdlv_margins(population = "fas_hcq") %>% 
  filter(analysis != 0) %>% 
  mutate(Explanation = if_else(analysis == 1, "Slope by treatment", "Difference in slope")) %>% 
  select(-analysis) %>%
  select(rantrt, Explanation, margin, ci_lb, ci_ub, pvalue) %>% 
  knitr::kable(col.names = c("Treatment",
                             "Explanation",
                              "Estimate",
                              "Lower 95% CL",
                              "Upper 95% CL",
                              "P-value"),
               digits = 3, caption = "Estimated treatment effect, HCQ")


```

#Dichotomous endpoints

## Hydroxychloroquine results

```{r dich, results = "asis"}

 di_f <- function(
                         var = "survcens",
                         population = "fas") {
  var_ <- ensym(var)
  population <- ensym(population)
  
  data <- addi %>%
    filter(!!population == "Yes" ) %>%
    mutate(rantrt = fct_drop(rantrt))
    
  
  x <- glue::glue(
    "
tempfile tmp1
tempfile tmp2


logistic {var} i.rantrt
margins i.rantrt, saving(`tmp1')
margins r.rantrt, saving(`tmp2')


use `tmp1', clear
append using `tmp2', gen(type)

"
  )
  
  margins <-  stata(
    src = x,
    data.in = data,
    data.out = TRUE,
    stata.path = "/usr/local/bin/stata-se",
    stata.version = 16,
    stata.echo = FALSE
  )
  
  res <- margins %>%
    rename_with(~ str_replace(.x, "_", "")) %>%
    select( margin, pvalue, ci_lb:type) %>%
    select( rantrt = m1, margin,  ci_lb, ci_ub, pvalue, type) %>% 
    mutate(across(margin:ci_ub, ~round(.x*100, digits = 1))) %>% 
    mutate(pvalue = round(pvalue, digits = 3))
  
  return(res)
  
}

  
addi <- adev %>% 
  select(subjectid, starts_with("fas"), rantrt, starts_with("survcens"), starts_with("progression"), starts_with("mv"), starts_with("sq_admis_max")) %>% 
  mutate(across(starts_with("survcens"), ~ if_else(.x == "No", 1, 0))) %>% 
  mutate(across(starts_with("progression"), ~ if_else(.x == "Yes", 1, 0))) %>%
  mutate(across(starts_with("mv"), ~ if_else(.x == "Yes", 1, 0))) %>% 
  mutate(across(starts_with("sq_admis_max"), ~ if_else(.x == "ICU", 1, 0))) 



rddi <- tibble(population = c("fas_hcq", "fas_rem")) %>% 
  crossing(var = c("survcens","survcens_60","survcens_28", "progression", 
                   "progression28", "progression60", "mv", "mv28", "mv60", 
                   "sq_admis_max", "sq_admis_max28", "sq_admis_max60")) %>% 
  mutate(dires = map2(var, population, di_f)) 

rddi %>% unnest(dires) %>% 
  knitr::kable()
  

```




# Inflammatory laboratory parameters



```{r efflbres, results = "asis", echo = FALSE}
rdlb <- read_rds("results/rds/rdlb.rds")



lables <- rdlb %>% 
  select(var) %>% 
  distinct() %>% 
  mutate(label =case_when(
    var == "lbcrpres" ~  "CRP (mg/L)",
    var == "lbferres" ~  "Ferritin (µg/L)",
    var == "lbldres" ~   "LDH (U/L)",    
    var == "lblymres" ~  "Lymphocytes (x10^9/L)",
    var == "lbneures" ~  "Neutrophils (x10^9/L)",
    var == "lbprores" ~  "Procalcitonin (µg/L)",
  ))

efflbres <- rdlb %>%
  select(-label) %>% 
  full_join(lables, by="var") %>% 
  mutate(poptitle = if_else(population == "fas_hcq", "HCQ", "Remdesivir")) %>% 
  mutate(marginsplot = pmap(list(data = margins, ytitle = label), plot_cont_margins),
         title = glue::glue("{label}, {poptitle}"))


efflbres %>%
  mutate(walk2(descriptives, title, ~knitr::kable(.x, caption = .y) %>% print),
         marginsplot = map2(marginsplot, title, ~ .x + ggtitle(.y) ),
         walk(marginsplot, print),
         walk2(diffs, title,  ~knitr::kable(.x, caption = .y,
                                            col.names = c("Treatment",
                                                          "Days since randomisation",
                                                          "Treatment difference",
                                                          "Lower 95% CL",
                                                          "Upper 95% CL",
                                                          "P-value"),
                                            digits = 3) %>%
                 print)
         )  %>%
  invisible()




```


# SARS-CoV2 antibodies at day 90

## Main results by quantreg

```{r antibodies}
library(quantreg) 
library(broom)
tdab <- read_rds("data/td/tdab.rds")

adab <- adsl %>% 
  left_join(tdab %>% select(subjectid, studyday, absumctr, abrbd, abace2rbd ), by = "subjectid") %>% 
  mutate(abnormrbd = abrbd/absumctr*100) %>% 
  filter(studyday >65) %>% 
  mutate(rantrt = factor(rantrt, ordered = FALSE))

lreg_f <- function(var = "abrbd", population = "fas"){
  # var <- ensym(var)
  population <- ensym(population)

  f.str <- paste0(var, " ~ rantrt")
  data <- adab %>%
    filter(!!population == "Yes") %>%
    mutate(rantrt = fct_drop(rantrt))
  #res <- rlang::qqshow(quantreg::rq(!!var ~ rantrt, data = data))
  res <- lm(as.formula(f.str), data = data) %>%
    tidy(conf.int = TRUE)

  return(res)
}
  

mreg_f <- function(var = "abrbd", population = "fas"){
  # var <- ensym(var)
  population <- ensym(population)

  f.str <- paste0(var, " ~ rantrt")
  data <- adab %>%
    filter(!!population == "Yes") %>%
    mutate(rantrt = fct_drop(rantrt))
  #res <- rlang::qqshow(quantreg::rq(!!var ~ rantrt, data = data))
  res <- suppressWarnings(quantreg::rq(as.formula(f.str), data = data)) %>%
    tidy(se = "boot", conf.int = TRUE, R=20000)

  return(res)
}

rdab <- tibble(
  population = c("fas_hcq", "fas_rem")
  ) %>%
  crossing(var = c("abrbd", "abnormrbd", "abace2rbd")) %>%
  mutate(res_m = map2(var, population, mreg_f),
         res_l = map2(var, population, lreg_f)) 

rdab %>%
  select(-res_l) %>% 
  unnest(res_m) %>%  
  knitr::kable(digits = 3)


  


```


## HCQ results from Stata

```{r antibodies-hcq}


 stata_qreg <-
    "
qreg abrbd i.rantrt
qreg abnormrbd i.rantrt
qreg abace2rbd i.rantrt

"

  stata(
    src = stata_qreg,
    data.in = adab %>% filter(fas_hcq == "Yes"),
    data.out = FALSE,
    stata.path = "/usr/local/bin/stata-se",
    stata.version = 16,
    stata.echo = TRUE
  )


  
  


```

## Remdesivir results by Stata

```{r antibodies-remdesivir}

 stata(
    src = stata_qreg,
    data.in = adab %>% filter(fas_hcq == "Yes"),
    data.out = FALSE,
    stata.path = "/usr/local/bin/stata-se",
    stata.version = 16,
    stata.echo = TRUE
  )


```


## Sensitivity results by ANOVA

```{r antibodies-sensitivity}


rdab %>%
  select(-res_m) %>% 
  unnest(res_l) %>%  
  knitr::kable(digits = 3)


```

# Time to last discharge

## Remdesivir

```{r discharge-rem}
library(survival)
library(survminer)
adev_rem <- adev %>% filter(fas_rem == "Yes")
fit_rem  <- surv_fit(Surv(dischargeday, dischargecens == "No") ~ rantrt, 
                      data = adev_rem)

ggsurvplot(fit_rem, data = adev_rem, fun = "event")

fit_rem_28  <- surv_fit (Surv(dischargeday_28, dischargecens_28 == "No") ~ rantrt, 
                      data = adev_rem)

ggsurvplot(fit_rem_28, data = adev_rem, fun = "event")

```
## HCQ

```{r discharge-hcq}
library(survival)
library(survminer)
adev_hcq <- adev %>% filter(fas_hcq == "Yes")
fit_hcq  <- surv_fit(Surv(dischargeday, dischargecens == "No") ~ rantrt, 
                      data = adev_hcq)

ggsurvplot(fit_hcq, data = adev_hcq, fun = "event")

fit_hcq_28  <- surv_fit (Surv(dischargeday_28, dischargecens_28 == "No") ~ rantrt, 
                      data = adev_hcq)

ggsurvplot(fit_hcq_28, data = adev_hcq, fun = "event")

```

# Adverse Events


## AE Summary

```{r ae-summary}

adae_fas <- adae %>% filter(fas =="Yes")

ae_summary_table <- tribble(
    ~text,  ~var, ~f,
  "Number of AEs", "anyae", "ae_N_n_pct",
  "Number of patients with any AEs?", "anyae", "ae_n_pct",
  "Number of patients with one AE", "one_ae", "ae_n_pct",
  "Number of patients with two AE", "two_ae", "ae_n_pct",
  "Number of patients with three or more AEs", "three_plus_ae", "ae_n_pct",
  "Number of SAEs", "sae", "ae_N_n_pct",
  "Number of patients with any SAEs?", "anysae","ae_n_pct"
)

tmp<-ae_summary_table %>%
  mutate(data = list(adae_fas),
         group = "rantrt",
         param = list(level = 1)) %>%
  mutate(res = pmap(list(f, data, var, group, param), stats_exec)) %>%
  mutate(id = map(res,names)) %>%
  unnest(c(res, id)) %>%
  mutate(id = paste0("txt", id)) %>%
  pivot_wider(values_from = res, names_from = id) %>%
  select(text, starts_with("txt")) %>%
  knitr::kable(col.names = c("Parameter", header_tot),
        caption = "Summary of Adverse Events")

tmp
```

The numbers are [Number of events] Number of patients (percentage of patients), or Number of patients (percentage of patients)


## By System Organ Class and Preferred Term

```{r aetab1}
ae_table_fns <- function(data, filtervar){

  filtervar = ensym(filtervar)

  data %>%
    group_by(rantrt) %>%
    mutate(N_pat = n_distinct(subjectid)) %>%
    filter(!!filtervar == 1)  %>%
    group_by(subjectid, rantrt, N_pat, soc_name, pt_name) %>%
    summarise(n_ae = n(),
              .groups = "drop_last") %>%
    filter(!is.na(pt_name)) %>%
    group_by(rantrt, N_pat, soc_name, pt_name) %>%
    summarise(n_pat = n(),
              n_ae = sum(n_ae),
              .groups = "drop_last") %>%
    mutate(pct = round(n_pat/N_pat*100,digits = 1),
           txt = paste0("[", n_ae,"] ", n_pat, " (", pct, "%)"),
           arm = rantrt) %>%
    ungroup %>% select(arm, soc_name, pt_name, txt) %>%
    pivot_wider(values_from = txt, names_from = arm, values_fill = list(txt = "")) %>%
    #mutate_at(vars(starts_with("arm")), ~if_else(is.na(.), "", .)) %>%
    arrange(soc_name, pt_name) %>%  group_by(soc2 = soc_name) %>%
    mutate(soc_name = if_else(row_number() != 1, "", soc_name)) %>% ungroup() %>% select(-soc2) %>%
    filter(soc_name != "NA")
}

adae_fas %>%
  bind_rows(adae_fas, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  mutate(all = 1) %>%
  ae_table_fns("all") %>%
  knitr::kable(col.names = c("System Organ Class", "Preferred Term", header_tot),
               caption = " Adverse Events by System Organ Class and Preferred term", longtable = TRUE, booktabs = TRUE) #%>%
  #column_spec(1:2, width = "5cm")
```

## Serious Adverse Events

```{r saetab}

adae_fas %>%
  bind_rows(adae, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  ae_table_fns("aesercd") %>%
  knitr::kable( col.names = c("System Organ Class", "Preferred Term", header_tot),
               caption = "Serious Adverse Events by System Organ Class and Preferred term",
         booktabs = TRUE,
         longtable = TRUE) #%>%
  #column_spec(1:2, width = "5cm")

```

## Suspected Unexpected Serious Adverse Reaction

```{r susar}

adae_fas %>%
  bind_rows(adae, .id="added") %>%
  mutate(pt_name = if_else(added == 2, "#Total", pt_name)) %>%
  mutate(susar = (aesercd == 1) & (saerelcd == 2) & saeexpcd ==2) %>%
  ae_table_fns("susar") %>%
  rename( "System Organ Class" = soc_name,  "Preferred Term" = pt_name) %>%
  knitr::kable(
               caption = "Suspected Unexpected Serious Adverse Reaction by System Organ Class and Preferred term",
         booktabs = TRUE,
         longtable = TRUE)

```

<!-- # Mortality and other outcomes by admission state -->

<!-- ```{r} -->
<!-- adeff %>% -->
<!--   group_by(sq_admis, outcome) %>% -->
<!--   summarise(n = n(), .groups = "drop_last") %>% -->
<!--   group_by(sq_admis) %>% -->
<!--   mutate(tot = sum(n), -->
<!--            pct = round(n/tot*100,digits = 1)) %>% -->
<!--   mutate(txt = paste0(n, " (", pct, "%)")) %>% -->
<!--   ungroup %>% -->
<!--   select(-(n:pct)) %>% -->
<!--   pivot_wider(values_from = txt, names_from = sq_admis) %>% -->
<!--   knitr::kable( booktabs = TRUE, caption = "Outcome") -->

<!-- ``` -->




<!-- # Outcome -->

<!-- The following report is based on pseudo-randomised groups, not true allocations. The true allocations are available for the DMC only. -->

<!-- ```{r outcome} -->

<!-- adeff %>% -->
<!--   mutate(rantrt = sample(rantrt, n(), replace = FALSE)) %>% #Delete this row for true allocations -->
<!--   group_by(rantrt, outcome) %>% -->
<!--   summarise(n = n(), .groups = "drop_last") %>% -->
<!--   group_by(rantrt) %>% -->
<!--   mutate(tot = sum(n), -->
<!--            pct = round(n/tot*100,digits = 1)) %>% -->
<!--   mutate(txt = paste0(n, " (", pct, "%)")) %>% -->
<!--   ungroup %>% -->
<!--   select(-(n:pct)) %>% -->
<!--   pivot_wider(values_from = txt, names_from = rantrt) %>% -->
<!--   knitr::kable(col.names = c("Parameter", header), booktabs = TRUE, caption = "Outcome") -->


<!-- ``` -->
